---
title: "index.Rmd"
author: "Hannah Gavin"
date: "12/5/2017"
output: html_document
---

```{r warning=FALSE, message=FALSE, echo=FALSE}
source('hannah_gavin_csv_data.R')
library(knitr)
```
# Table of Seattle Neighborhood Data
This is a summary table of our data on Seattle's neighborhoods.

```{r eval=TRUE, echo=FALSE}
kable(all.summary.data)
```

# Summary of Neighborhood Data

Here are some key takeaways from the table above. There are a total of `r sum(all.summary.data$"Number of Bike Racks")` bike racks in Seattle. Out of the `r nrow(all.summary.data)` neighborhoods, only `r length(which(!is.na(all.summary.data$"Number of Public Spaces")))` have public spaces. The neighborhood with the most public garages and parking lots is `r all.summary.data[which.max(all.summary.data$"Number of Garages and Parking Lots"), "Neighborhood"]` with `r all.summary.data[which.max(all.summary.data$"Number of Garages and Parking Lots"), "Number of Garages and Parking Lots"]` total. The average number of food banks and tennis courts per neighboorhood in Seattle are `r sum(all.summary.data$"Number of Food Banks", na.rm = TRUE)/nrow(all.summary.data)` and `r sum(all.summary.data$"Number of Tennis Courts", na.rm = TRUE)/nrow(all.summary.data)`, respectively.
